# Regression Model on mtcars Dataset
Xiangzhu Long

## Context
Looking at a data set of a collection of cars, exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). Try to figure out the following two questions:

1.Is an automatic or manual transmission better for MPG?

2.Quantify the MPG difference between automatic and manual transmissions.

## Is an automatic or manual transmission better for MPG?
```{r}
data(mtcars)

mtcars$am <- as.factor(mtcars$am)
levels(mtcars$am) <-c("Automatic", "Manual")

t.test(mtcars$mpg~mtcars$am,conf.level=0.95)

```
The p-value is 0.001374, we may think it is ok to reject the null hypothesis and conclude automatic has low mpg compared with manual cars - however this assumption is based on all other characteristics of auto cars and manual cars are same  - which needs to be further explored in the multiple linear regression analysis.


## Quantifying how different is the MPG between automatic and manual transmissions?
```{r}
stepmodel = step(lm(data = mtcars, mpg ~ .),trace=0,steps=10000)
summary(stepmodel)

model <- lm(mpg~ factor(am):wt + factor(am):qsec,data=mtcars)
summary(model)
```


## Conclusions

According to these results, cars with a manual transmission are better for mpg than cars with an automatic transmission. The rate of change of the conditional mean mpg with respect to am is about 1.8, and we are 95% confident that this value varies between -1.06 and 4.68. 

## Appendix
```{r}
boxplot(mtcars$mpg ~ mtcars$am, data = mtcars, outpch = 19, ylab="mpg:miles per 
gallon",xlab="transmission type",main="mpg vs transmission type")
```


```{r}
par(mfrow=c(2, 2))
plot(model)
```
