# Analysis on Inferential Data
Xiangzhu Long


## Introduction
We're going to analyze the ToothGrowth data in the R datasets package and make a basic summary of the data, like using confidence intervals and hypothesis tests to compare tooth growth by supp and dose. 


## Stimulation
```{r}
# Load dependencies
library(ggplot2)
set.seed(7)

# Load the ToothGrowth data
data(ToothGrowth)
head(ToothGrowth)
```


## Analysis
```{r}
# Comparing the data sets
ggplot(ToothGrowth, aes(x = len, fill = supp)) + 
  facet_wrap(~dose) + scale_fill_brewer(palette = 'Set1') + 
  xlab('tooth length') + ggtitle('Distribution of Guinea_pig Tooth Lengths') + 
  geom_histogram()

summary(ToothGrowth)

# compare tooth growth by supp and dose.
supp.t1 <- t.test(len~supp, paired=F, var.equal=T, data=ToothGrowth)
supp.t2 <- t.test(len~supp, paired=F, var.equal=F, data=ToothGrowth)
supp.result <- data.frame("p-value"=c(supp.t1$p.value, supp.t2$p.value),
                          "Conf-Low"=c(supp.t1$conf[1],supp.t2$conf[1]),
                          "Conf-High"=c(supp.t1$conf[2],supp.t2$conf[2]),
                          row.names=c("Equal Var","Unequal Var"))
supp.result
```


## Results
Based on the sample data provided:

1.At lower dosages (.5 Mg - 1 Mg), orange juice provides more tooth growth than ascorbic acid.

2.At the higher dosage (2 Mg), the rate of tooth growth is not statistically different between supplement methods.

3.Regardless of the supplement method, dosage is a key factor in tooth growth.



